Competing Bandits: The Perils of Exploration under Competition

### 2018-09-05 paper/content/model.tex
new plot...also fix computation details

\item \emph{Uniform instance}: the mean reward of each arm is drawn independently and uniformly from $[0.25, 0.75]$.
\item \emph{Heavy-tail instance}: the mean reward of each arm is drawn independently from $\Beta(.6,.6)$ distribution.%
    \footnote{This distribution has substantial ``tail probabilities".}
\end{enumerate}
We argue that these MAB instances are (somewhat) representative. Consider the ``gap" between the best and the second-best arm, an essential parameter in the literature on MAB. The ``gap" is fixed in Needle-in-Haystack, spread over a wide spectrum of values under the Uniform instance, and is spread but  focused on the large values under the Heavy-Tail instance.

@@

The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 2200Hz CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about 10.5 hours.

>>>>

\item \emph{Uniform instance}: the mean reward of each arm is drawn independently and uniformly from $[0.25, 0.75]$.
\item \emph{Heavy-tail instance}: the mean reward of each arm is drawn independently from $\Beta(.6,.6)$ distribution.%
    \footnote{This distribution has substantial ``tail probabilities".}
\end{enumerate}
We argue that these MAB instances are (somewhat) representative. Consider the ``gap" between the best and the second-best arm, an essential parameter in the literature on MAB. The ``gap" is fixed in Needle-in-Haystack, spread over a wide spectrum of values under the Uniform instance, and is spread but  focused on the large values under the Heavy-Tail instance. \asedit{We also ran smaller experiments with versions of these instances, and achieved similar qualitative results.}

@@

The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 2.2 GHz CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about $10$ hours.
